Record of Commands Used 

```{r}
#Loading in neccesary packages (Make sure you actually have them, using the same package names but "load" instead of "library")
library(dplyr)
library(ggplot2)
library(tidyr)
library(statsr)
```

```{r}

setwd("~/Gender Project/R Files") #You won't have the same file path as me. Put all the csv files into one place, then set that place as the working directory in the bottom right panel of RStudio (The "more" option with the metal cog)
#arXiv datasets
arxivF <- read.csv(file= "arxivF.csv")
arxivL <- read.csv(file= "arxivL.csv")
#bioRxiv/medRxiv datasets
bioRxivF <- read.csv(file= "bioRxivF.csv")
bioRxivL <- read.csv(file= "bioRxivL.csv")
#dataset for limitation figure
MCO <- read.csv(file= "MCO.csv")
```

-----------------------------------------------
TRIMMING OF RAW DATA
```{r}
#Selecting only 2017-2020
yr <- c("2017","2018","2019","2020") 

#Remove all names with database n<10
bioRxivF <- bioRxivF %>% filter(Samples >=10) 

#Remove all name accuracy below 95, and select all years between 2017-2020
bioRxivF_ <- bioRxivF %>% filter(Year %in% yr, Accuracy >=95)

#Change the text for the "Name" column for aesthetic purposes.
bioRxivF_ <- bioRxivF_ %>% mutate(Name = ï..Name)
bioRxivF_ <- select (bioRxivF_,-c(ï..Name))

#Create a table with only the Biorxiv and Medrxiv covid-related papers
FC<- bioRxivF_ %>% filter(Topic == "COVID") 

#Create a table with the opposite, remove any papers labelled "C" (As they are simply "COVID" topic paper repeats, grouped into their actual submitted topics)
FN<- bioRxivF_ %>% filter(Topic != "COVID", Covid !="C") 

#Bind the two to make a new dataset with no repeats and the neccessary trimming
bioRxivF_ <- rbind(FC,FN) #Merge the two cells to recreate original table, now with no COVID-19 Paper repeats


```

-------------------------------------------------
TABLES FOR FIGURE 1
```{r}
#Rename the table for organizational purposes
Fig1<- filter(bioRxivF_, Server != "Medrxiv")

#Prepare dataset for graphing by grouping into year, month sex and summarizing total males/females in each.
PROP_SEXF <- Fig1 %>% group_by(Year, Month, Sex) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), 

#making the N count label seen on figure 1
flabel=ifelse(Sex=="female", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3)) 

#Remove all male entries, so that female freq can be graphed individually.
PROP_SEXF <- PROP_SEXF %>% filter(Sex=="female") 
```

----------------------------------------
TABLES FOR MANUAL STATISTICAL TESTS
```{r}
#Making files with just biorxiv, medrxiv or COVID papers for external statistical calculations. (To proof-check the RStudio Calculations)
CSVFBiorxiv <- filter(bioRxivF, Samples >=10, Accuracy >=95, Server== "Biorxiv", Topic!="COVID", Covid !="C") 
CSVFMedrxiv <- filter(bioRxivF, Samples >=10, Accuracy >=95, Server== "Medrxiv")
CSVFCOVID <- filter(bioRxivF, Samples >=10, Accuracy >=95, Topic=="COVID")
CSVF2020 <- filter(bioRxivF_, Samples >=10, Accuracy >=95, Year =="2020")

#Grouping names based on specific variables, summarizing total N in each bin.

CSVFBiorxiv <-group_by(CSVFBiorxiv, Month, Topic, Year, Sex)%>% summarise(n=n())
CSVFMedrxiv <-group_by(CSVFMedrxiv, Month, Topic, Year, Sex)%>% summarise(n=n())
CSVFCOVID <-group_by(CSVFCOVID, Server, Month, Sex)%>% summarise(n=n())
CSVF2020 <-group_by(CSVF2020, Server, Month, Sex)

#Saving each as a CSV file, so that it can be sent for analysis through other means.

#write.csv(CSVFBiorxiv, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\Firstnamebiorxiv.csv", row.names=TRUE)
#write.csv(CSVFMedrxiv, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\Firstnamemedrxiv.csv", row.names=TRUE)
#write.csv(CSVFCOVID, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\FirstnameCOVID.csv", row.names=TRUE)
#write.csv(CSVF2020, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\CSVF2020.csv", row.names=TRUE)
```

------------------------------------
FIGURE 1
```{r}
#Function to autosave file, so it can be updated on the paper automatically.
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig1.jpeg", quality=100, height= 480, width = 720)


#Graph for figure 1
ggplot(PROP_SEXF[order(PROP_SEXF$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female first author percentage for all Jan,April,May bioRxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=flabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```


```{r}
#Graph for figure 1
ggplot(PROP_SEXF[order(PROP_SEXF$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female first author percentage for all Jan,April,May bioRxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=flabel),position=position_dodge(width=0.9), vjust=-0.5, size=2.5)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

STATISTICAL TESTS (As seen in Figure 1 Legend)
```{r}
#Grouping the matrix into respective months
Fig1J <- filter(Fig1, Month == "January")
Fig1A <- filter(Fig1, Month == "April")
Fig1M <- filter(Fig1, Month == "May")

#Chi-sq test for each month, all years
chisq.test(Fig1J$Year, Fig1J$Sex, correct=FALSE)
chisq.test(Fig1A$Year, Fig1A$Sex, correct=FALSE)
chisq.test(Fig1M$Year, Fig1M$Sex, correct=FALSE)

#isolating for only 2019 and 2020
Yr <-c("2019","2020")

Fig1JY <- filter(Fig1J, Year %in% Yr)
Fig1AY <- filter(Fig1A, Year %in% Yr)
Fig1MY <- filter(Fig1M, Year %in% Yr)

#Two proportion t-test (Same calculation and p value as chi-sq, but only 2 years so this one is better)
inference(y = Sex, x = Year, data = Fig1JY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig1AY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig1MY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")

#Chi squared test if you want to verify that the same p value is returned as above.
chisq.test(Fig1JY$Year, Fig1JY$Sex, correct=FALSE)
chisq.test(Fig1AY$Year, Fig1AY$Sex, correct=FALSE)
chisq.test(Fig1MY$Year, Fig1MY$Sex, correct=FALSE)
```

----------------------------------------
FIGURE 3A
```{r}
#Renaming to Fig3A for organizational purposes
Fig3A <-bioRxivF_ 

#Making new COVID-determinant variable for aesthetic purposes (for the figure)
Fig3A <- mutate(Fig3A, COVID= ifelse(Covid=="C" , "COVID-19", "Other")) 

#Removing all years except 2020 for comparitive purposes.
Fig3A <-filter(Fig3A, Year == "2020") 

#Making a table comparing frequency of each sex for the Covid vs Other papers.
fig3A <- Fig3A %>% group_by(COVID,Sex) %>% summarize(n=n()) %>% mutate(Perc= n/sum(n)) 

#Adding extra columns for labelling purposes (On the graph)
fig3A <- fig3A %>% mutate(frequency = round(Perc, digits = 3)) %>% mutate(freq= n/sum(n), cumul.sum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))
fig3A$labelpos <- ifelse(fig3A$Sex=="female", fig3A$frequency/2, 1 - fig3A$frequency/2)

#Saving figure 3A
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig3A.jpeg", quality=100)

#Making figure 3a
ggplot(fig3A[order(fig3A$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + xlab("Subject of Paper") + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())

#Chi Squared test for COVID-related vs other papers, female proportion
chisq.test(Fig3A$COVID, Fig3A$Sex, correct=FALSE)

#Converting COVID to factor variable

```

```{r}
#Alternative test for the above figure, and repeat of figure for viewing purposes.
inference(y = Sex, x = COVID, data = Fig3A, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
ggplot(fig3A[order(fig3A$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + xlab("Subject of Paper") + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("First author sex representation for COVID-19 and other papers (All)") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```





EXACT SAME CODE, BUT FOR LAST NAME(ALL CODE DESCRIPTION CAN BE FOUND IN THE ABOVE CODE)
```{r}
bioRxivL <- bioRxivL %>% filter(Samples >=10) 
bioRxivL_ <- bioRxivL %>% filter(Samples >=10, Accuracy >= 95, Year %in% yr) 
bioRxivL_ <- bioRxivL_ %>% mutate(Name = ï..Name) 
bioRxivL_ <- select (bioRxivL_,-c(ï..Name))
LC<- bioRxivL_ %>% filter(Topic == "COVID") 
LN<- bioRxivL_ %>% filter(Topic != "COVID", Covid !="C") 
bioRxivL_ <- rbind(LC,LN) 
```

```{r}
Fig2<- filter(bioRxivL_, Server != "Medrxiv")
PROP_SEXL <- Fig2 %>% group_by(Year, Month, Sex) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), 
llabel=ifelse(Sex=="female", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3)) 
PROP_SEXL <- PROP_SEXL %>% filter(Sex=="female") 
```

```{r}
CSVLBiorxiv <- filter(bioRxivL, Samples >=10, Accuracy >=95, Server== "Biorxiv", Topic!="COVID", Covid !="C")
CSVLMedrxiv <- filter(bioRxivL, Samples >=10, Accuracy >=95, Server== "Medrxiv")
CSVLCOVID <- filter(bioRxivL, Samples >=10, Accuracy >=95, Topic=="COVID")
CSVL2020 <- filter(bioRxivL_, Samples >=10, Accuracy >=95, Year =="2020")
CSVLBiorxiv <-group_by(CSVLBiorxiv, Month, Topic, Year, Sex)%>% summarise(n=n())
CSVLMedrxiv <-group_by(CSVLMedrxiv, Month, Topic, Year, Sex)%>% summarise(n=n())
CSVLCOVID <-group_by(CSVLCOVID, Server, Month, Sex)%>% summarise(n=n())
CSVL2020 <-group_by(CSVL2020, Server, Month, Sex)
#write.csv(CSVLBiorxiv, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\Lastnamebiorxiv.csv", row.names=TRUE)
#write.csv(CSVLMedrxiv, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\Lastnamemedrxiv.csv", row.names=TRUE)
#write.csv(CSVLCOVID, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\LastnameCOVID.csv", row.names=TRUE)
#write.csv(CSVL2020, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\CSVL2020.csv", row.names=TRUE)
```

FIGURE 2
```{r}

#Graph for Figure 2
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig2.jpeg", quality=100, height=480, width=720)
ggplot(PROP_SEXL[order(PROP_SEXL$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female last author percentage for all Jan,April,May bioRxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=llabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```
```{r}
ggplot(PROP_SEXL[order(PROP_SEXL$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female last author percentage for all Jan,April,May bioRxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=llabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

STATISTICAL TESTS FOR FIGURE 2
```{r}
Fig2J <- filter(Fig2, Month == "January")
Fig2A <- filter(Fig2, Month == "April")
Fig2M <- filter(Fig2, Month == "May")
Yr <-c("2019","2020")
Fig2JY <- filter(Fig2J, Year %in% Yr)
Fig2AY <- filter(Fig2A, Year %in% Yr)
Fig2MY <- filter(Fig2M, Year %in% Yr)
chisq.test(Fig2J$Year, Fig2J$Sex, correct=FALSE)
chisq.test(Fig2A$Year, Fig2A$Sex, correct=FALSE)
chisq.test(Fig2M$Year, Fig2M$Sex, correct=FALSE)
inference(y = Sex, x = Year, data = Fig2JY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig2AY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig2MY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
prop.test(x=c(361,475), n=c(1720,2128), p = NULL, alternative = "two.sided", correct = TRUE)
chisq.test(Fig2JY$Year, Fig2JY$Sex, correct=FALSE)
chisq.test(Fig2AY$Year, Fig2AY$Sex, correct=FALSE)
chisq.test(Fig2MY$Year, Fig2MY$Sex, correct=FALSE)
```

FIGURE 3B
```{r}
Fig3B <-bioRxivL_
Fig3B <- mutate(Fig3B, COVID= ifelse(Covid=="C" , "COVID-19", "Other"))
Fig3B <-filter(Fig3B, Year == "2020")
fig3B <- Fig3B %>% group_by(COVID,Sex) %>% summarize(n=n()) %>% mutate(Perc= n/sum(n))
```

```{r}
fig3B <- fig3B %>% mutate(frequency = round(Perc, digits = 3)) %>% mutate(freq= n/sum(n), cumul.sum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))
fig3B$labelpos <- ifelse(fig3B$Sex=="female", fig3B$frequency/2, 1 - fig3B$frequency/2)
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig3B.jpeg", quality=100)
ggplot(fig3B[order(fig3B$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + geom_bar(position="stack",stat="identity") + xlab("Subject of Paper") +ylab("Percentage") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```
VIEWING FIGURE3B
```{r}
ggplot(fig3B[order(fig3B$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + geom_bar(position="stack",stat="identity") + xlab("Subject of Paper") +ylab("Percentage")+ggtitle("Last author sex representation for COVID-19 and other papers (All)") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
chisq.test(Fig3B$COVID, Fig3B$Sex, correct=FALSE)
inference(y = Sex, x = COVID, data = Fig3B, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
```



CODE FOR FIRST AUTHOR ARXIV DATA (PHYSICS, MATHEMATICS, STATISTICS)

----------------------------------------------------------------------------
RAW DATA TRIMMING
```{r}
#Mutating Covid so it produces "COVID-19" and "Other" instead of "C" and " ", filtering based on previously mentioned parameters.
arxivF<- arxivF %>% mutate(Name=ï..Name)
arxivF<- arxivF %>% filter(Samples >=10, Accuracy >= 95, !is.na(Name)) %>% mutate(COVID = ifelse(Covid == "C", "COVID-19", "Other")) 
```

-----------------------------------------------------------------------
TABLES FOR FIGURE 4A
```{r}
#Rename the matrix for organizational purposes
Fig4A<- arxivF 

 # Prepare dataset for graphing 
APROP_SEXF <- Fig4A %>% group_by(Year, Month, Sex) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq),
#making the N count label

aflabel=ifelse(Sex=="female", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3)) 
#Remove all male entries, so that freq can be graphed side-by side.

APROP_SEXF <- APROP_SEXF %>% filter(Sex=="female") 
```

-----------------------------------------------------------------------
TABLES FOR Manual Stat Tests
```{r}
#Making file for external statistical calculations. (To proof-check the RStudio Calculations)
ArxivCOVIDF <- filter(arxivF, Samples >=10, Accuracy >=95, COVID=="COVID-19") 
ArxivOtherF <- filter(arxivF, Samples >=10, Accuracy >=95, COVID=="Other")

#Making the tables into relevant groups, summarizing the total amount of names that fall into each category

ArxivCOVIDF <-group_by(ArxivCOVIDF, Month, Topic, Year, Sex)%>% summarise(n=n())
ArxivOtherF <-group_by(ArxivOtherF, Month, Topic, Year, Sex)%>% summarise(n=n())

#Saving each as a CSV file, so that it can be sent for analysis through other means.

#write.csv(ArxivCOVIDF, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\ArxivCovidF.csv", row.names=TRUE)
#write.csv(ArxivOtherF, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\ArxivOtherF.csv", row.names=TRUE)
```

----------------------------------------------------------------------------
Figure 4A
```{r}
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig4A.jpeg", quality=100, height= 480, width = 720)
#Graph for Figure4A
ggplot(APROP_SEXF[order(APROP_SEXF$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female first author percentage for Jan,April,May arxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=aflabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

TO VIEW FIGURE 4A
```{r}
ggplot(APROP_SEXF[order(APROP_SEXF$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female first author percentage for Jan,April,May arxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=aflabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

--------------------------------------
STATISTICAL TESTS FOR FIGURE4A
```{r}
#Statistical Tests (THE MAY PART IS PUT IN BRACKETS AS WE HAVE NOT FINISHED COLLECTING THE DATA FOR MAY)

#Organizing into each month
Fig4AJ <- filter(Fig4A, Month == "January")
Fig4AA <- filter(Fig4A, Month == "April")
Fig4AM <- filter(Fig4A, Month == "May")

#Chi-sq test for 2017-2020, female proportion
chisq.test(Fig4AJ$Year, Fig4AJ$Sex, correct=FALSE)
chisq.test(Fig4AA$Year, Fig4AA$Sex, correct=FALSE)
chisq.test(Fig4AM$Year, Fig4AM$Sex, correct=FALSE)

#Selecting only 2019 and 2020
Yr <-c("2019","2020")

Fig4AJY <- filter(Fig4AJ, Year %in% Yr)
Fig4AAY <- filter(Fig4AA, Year %in% Yr)
Fig4AMY <- filter(Fig4AM, Year %in% Yr)

#Two-prop T-test (Same as Chi-Sq with only 2 years)
inference(y = Sex, x = Year, data = Fig4AJY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig4AAY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig4AMY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")

#Same as above, to verify that same p value is produced
chisq.test(Fig4AJY$Year, Fig4AJY$Sex, correct=FALSE)
chisq.test(Fig4AAY$Year, Fig4AAY$Sex, correct=FALSE)
chisq.test(Fig4AMY$Year, Fig4AMY$Sex, correct=FALSE)
```



-----------------------------
FIGURE 5A
```{r}

#Renaming to Fig5A for organizational purposes
Fig5A <-arxivF 

 #Making new COVID-determinant variable for graphing.
Fig5A <- mutate(Fig5A, COVID= ifelse(Covid=="C" , "COVID-19", "Other"))

#Removing all years except 2020 for comparitive purposes.
Fig5A <-filter(Fig5A, Year == "2020") 

#Making a table comparing frequency of each sex for the Covid vs Other papers.
fig5A <- Fig5A %>% group_by(COVID,Sex) %>% summarize(n=n()) %>% mutate(Perc= n/sum(n)) 

#Making a proportional barplot:
fig5A <- fig5A %>% mutate(frequency = round(Perc, digits = 3)) %>% mutate(freq= n/sum(n), cumul.sum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))

fig5A$labelpos <- ifelse(fig5A$Sex=="female", fig5A$frequency/2, 1 - fig5A$frequency/2)

jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig5A.jpeg", quality=100)
ggplot(fig5A[order(fig5A$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + xlab("Subject of Paper") + geom_bar(position="stack",stat="identity") + ylab("Percentage") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

------------------------
FIGURE 5A
```{r}
#View plot 
ggplot(fig5A[order(fig5A$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + xlab("Subject of Paper") + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("First author sex representation for COVID-19 and other papers (All)") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())

#Chi sq test comparing COVID relatedness and female proportion
chisq.test(Fig5A$COVID, Fig5A$Sex, correct=FALSE)


#Same as above test, for double verification
inference(y = Sex, x = COVID, data = Fig5A, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
```



------------------------------------------------------------------------------------------
LAST NAME(SEE FIRST NAME FOR DESCRIPTION OF CODE)
```{r}
arxivL<- arxivL %>% mutate(Name=ï..Name)
arxivL<- arxivL %>% filter(Samples >=10, Accuracy >= 95, !is.na(Name)) %>% mutate(COVID = ifelse(Covid == "C", "COVID-19", "Other")) 
```

```{r}
Fig4B<- arxivL 
APROP_SEXL <- Fig4B %>% group_by(Year, Month, Sex) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), 
allabel=ifelse(Sex=="female", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3))
APROP_SEXL <- APROP_SEXL %>% filter(Sex=="female") 
```

```{r}
ArxivCOVIDL <- filter(arxivL, Samples >=10, Accuracy >=95, COVID=="COVID-19") 
ArxivOtherL <- filter(arxivL, Samples >=10, Accuracy >=95, COVID=="Other")
ArxivCOVIDL <-group_by(ArxivCOVIDL, Month, Topic, Year, Sex)%>% summarise(n=n())
ArxivOtherL <-group_by(ArxivOtherL, Month, Topic, Year, Sex)%>% summarise(n=n())
#write.csv(ArxivCOVIDL, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\ArxivCovidL.csv", row.names=TRUE)
#write.csv(ArxivOtherL, "C:\\Users\\adamw\\Documents\\Gender Project\\R Code\\ArxivOtherL.csv", row.names=TRUE)
```

FIGURE4B
```{r}
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig4B.jpeg", quality=100, height= 480, width = 720)
ggplot(APROP_SEXL[order(APROP_SEXL$Month, decreasing  = T),], aes(fill= factor(Month, levels=c("January","April","May" ) ), x=Year, y=freq)) + geom_bar(position="dodge",stat="identity") + ylab("Percentage")+ggtitle("Female Last author percentage for Jan,April,May arxiv articles") + scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("darkslategray3", "indianred3","darkolivegreen2"))+ theme(legend.title = element_blank())+ geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=15,size=3) + geom_text(aes(y=cumul.sum, label=allabel),position=position_dodge(width=0.9), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

STAT TESTS FOR FIGURE 4B
```{r}
Fig4BJ <- filter(Fig4B, Month == "January")
Fig4BA <- filter(Fig4B, Month == "April")
Fig4BM <- filter(Fig4B, Month == "May")
chisq.test(Fig4BJ$Year, Fig4BJ$Sex, correct=FALSE)
chisq.test(Fig4BA$Year, Fig4BA$Sex, correct=FALSE)
chisq.test(Fig4BM$Year, Fig4BM$Sex, correct=FALSE)
Yr <-c("2019","2020")
Fig4BJY <- filter(Fig4BJ, Year %in% Yr)
Fig4BAY <- filter(Fig4BA, Year %in% Yr)
Fig4BMY <- filter(Fig4BM, Year %in% Yr)
inference(y = Sex, x = Year, data = Fig4BJY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig4BAY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
inference(y = Sex, x = Year, data = Fig4BMY, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
chisq.test(Fig4BJY$Year, Fig4BJY$Sex, correct=FALSE)
chisq.test(Fig4BAY$Year, Fig4BAY$Sex, correct=FALSE)
chisq.test(Fig4BMY$Year, Fig4BMY$Sex, correct=FALSE)
```

FIGURE5B
```{r}
Fig5B <-arxivL 
Fig5B <- mutate(Fig5B, COVID= ifelse(Covid=="C" , "COVID-19", "Other")) 
Fig5B <-filter(Fig5B, Year == "2020") 
fig5B <- Fig5B %>% group_by(COVID,Sex) %>% summarize(n=n()) %>% mutate(Perc= n/sum(n)) 
fig5B <- fig5B %>% mutate(frequency = round(Perc, digits = 3)) %>% mutate(freq= n/sum(n), cumul.sum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))
fig5B$labelpos <- ifelse(fig5B$Sex=="female", fig5B$frequency/2, 1 - fig5B$frequency/2)
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig5B.jpeg", quality=100)
ggplot(fig5B[order(fig5B$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=COVID, y=Perc)) + xlab("Subject of Paper") + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

```{r}
chisq.test(Fig5B$COVID, Fig5B$Sex, correct=FALSE)

inference(y = Sex, x = COVID, data = Fig5B, statistic = "proportion", type = "ht", null = 0, 
          alternative = "twosided" , success = "female", method = "theoretical")
```
















(SUPPLEMENTARY Figures)

--------------------------------------
FIGURE 6
```{r}
#Reload bioRxivF in
setwd("~/Gender Project/R Files") 
#Re-Reading Original Dataset
bioRxivF <- read.csv(file= "biorXivF.csv")

#Using original dataset without 95% accuracy cutoff, removing COVID repeat papers through methods previously discussed
FC3<- bioRxivF %>% filter(Topic == "COVID", Samples>=10) 
FN3<- bioRxivF %>% filter(Topic != "COVID", Covid !="C", Samples>=10) 
Fig6 <- rbind(FC3,FN3)

# Creating multiple datasets with female-male ration at various cutoff levels
F_50 <- Fig6 %>% filter(Accuracy >= 50) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale) %>% mutate(Accuracy_Level = 50)
F_55 <- Fig6 %>% filter(Accuracy >= 55) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 55)
F_60 <- Fig6 %>% filter(Accuracy >= 60) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 60)
F_65 <- Fig6 %>% filter(Accuracy >= 65) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 65)
F_70 <- Fig6 %>% filter(Accuracy >= 70) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 70)
F_75 <- Fig6 %>% filter(Accuracy >= 75) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 75)
F_80 <- Fig6 %>% filter(Accuracy >= 80) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 80)
F_85 <- Fig6 %>% filter(Accuracy >= 85) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 85)
F_90 <- Fig6 %>% filter(Accuracy >= 90) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 90)
F_95 <- Fig6 %>% filter(Accuracy >= 95) %>% summarize(nfem= length(Sex[Sex=="female"]),nmale= length(Sex[Sex=="male"]),femratio= nfem/nmale)%>% mutate(Accuracy_Level = 95)
	
fig6 <- rbind(F_50, F_55, F_60, F_65, F_70, F_75, F_80, F_85, F_90, F_95)

#Merging all female-male ratios
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig6.jpeg", quality=100, height=480, width = 720)
ggplot(fig6, aes(x=Accuracy_Level, y=femratio)) + geom_point() + geom_line() + ggtitle("Ratio of Female-Male First Author Based on Accuracy cutoff") + ylab("Female:Male Ratio") + xlab("Name-Sex Accuacy") + ylim(0,1)


#making two matrices for comparing the female-male ratio statistically for all accuracy vs the utilized 95% accuracy

iF_50 <- Fig6 %>% filter(Accuracy >= 50) %>%  mutate(Accuracy_Level = 50)
iF_95 <- Fig6 %>% filter(Accuracy >= 95) %>%  mutate(Accuracy_Level = 95)
ifig6 <- rbind(iF_50, iF_95) 
```

FIGURE 7
```{r}

#Reload Biorxiv Dataset
setwd("~/Gender Project/R Files") 
bioRxivF <- read.csv(file= "biorXivF.csv")
bioRxivL <- read.csv(file= "bioRxivL.csv")
#Selecting articles with year 2016-2020 (As in the preprint servers, some errors occur when taking articles from arXiv and bioRxiv in this respect.
yr <- c("2017","2018","2019","2020") 

#Making matrics with all names processed through GenderAPI, and then same GenderAPI names, but put through the following conditions: Name-Sex Accuracy >95, Sample size of specific name in database >10

FNB <- bioRxivF%>% filter(Server == "Biorxiv",Year %in% yr) %>% summarize(n=n()) %>% mutate(Cut="All", AuthorPosition= "First Author") 
LNB<- bioRxivL%>% filter(Server == "Biorxiv",Year %in% yr) %>% summarize(n=n())  %>% mutate(Cut="All", AuthorPosition= "Last Author")
FNA <- arxivF%>% filter(Year %in% yr)  %>% summarize(n=n()) %>% mutate(Cut="All", AuthorPosition= "First Author")
LNA <- arxivL %>% filter(Year %in% yr) %>% summarize(n=n()) %>% mutate(Cut="All", AuthorPosition= "Last Author")
FNTB <- bioRxivF %>% filter(Server == "Biorxiv",Year %in% yr, Accuracy >=95, Samples>=10)%>% summarize(n=n()) %>% mutate(Cut="Trimmed", AuthorPosition= "First Author") 
LNTB <- bioRxivL %>% filter(Server == "Biorxiv",Year %in% yr, Accuracy >=95, Samples>=10)%>% summarize(n=n()) %>% mutate(Cut="Trimmed", AuthorPosition= "Last Author")
FNTA <- arxivF %>% filter(Year %in% yr, Accuracy >=95, Samples>=10)%>% summarize(n=n()) %>% mutate(Cut="Trimmed", AuthorPosition= "First Author")
LNTA <- arxivL %>% filter(Year %in% yr, Accuracy >=95, Samples>=10)%>% summarize(n=n())%>% mutate(Cut="Trimmed", AuthorPosition= "Last Author")

#Merging, and determining % of papers preserved by dividing by original N.
BFNG <- rbind(FNB,FNTB)
BFNG <- mutate(BFNG, freq=n/29735, Server="bioRxiv")

BLNG <- rbind(LNB,LNTB)
BLNG <- mutate(BLNG, freq=n/29588, Server="bioRxiv")

AFNG <- rbind(FNA,FNTA)
AFNG <- mutate(AFNG, freq=n/71349, Server="arXiv")

ALNG <- rbind(LNA,LNTA)
ALNG <- mutate(ALNG, freq=n/71362, Server="arXiv")

FIG7 <- rbind(BFNG, BLNG, AFNG, ALNG)

FIG7 <- filter(FIG7, Cut == "Trimmed")

#Preparing dataset for graphing
FIG7 <- FIG7 %>% mutate(frequency = round(freq, digits = 4),Flabel=ifelse(Cut=="Trimmed", paste0("N=", n ,""))) 

#Plot

jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\FIG7.jpeg", quality=100, height= 480, width = 720)
ggplot(FIG7, aes(fill= AuthorPosition, y=freq, x=Server)) + geom_bar(position="dodge",stat="identity") + ylab("Percent of Names Retained")+ xlab("Preprint Server") +ggtitle("Author Retention Based on GenderAPI Confidence Cutoff") + scale_y_continuous(labels = scales::percent, limits = c(0,1)) +theme_light() +scale_fill_manual(values= c("mediumseagreen", "darkorange1"))  + geom_text(aes(label= paste0(100*frequency,"%")), position=position_dodge(width=0.9), vjust=12.5,size=5) +labs(fill = "Author Position") +theme(text=element_text(size=17)) # + geom_text(aes(y=freq, label=Flabel), vjust=-0.5, size=3) (IF YOU WANT TO SEE REMAINING N COUNT)
```


FIGURE 8

MCO is an abbreviation for "Microbiology Continental Origin"
```{r}
#RemovingAll blank name spaces, due to GENDERAPI name errors. 
MCO <- MCO %>% filter( !is.na(Name), !is.na(Continent)) %>% mutate("Cutoff" = "All") 

#Creating a "cutoff" matrix, with all names that satisfy the normal cutoff parameters (database size >=10, name-sex accuracy >=95%)
MCOcutoff <- MCO %>% filter(Samples >=10, Accuracy >= 95, Year %in% yr) %>%mutate(Cutoff="Above")

#Creating a matrix with all the names that get cut off by standard parameters
MCOreverse <- MCO %>% filter(Accuracy <= 95, Year %in% yr) %>% mutate(Cutoff="Below")

#Creating a matrix for the "all" column in the figure produced at the end of this section
MCOb <-rbind(MCOcutoff,MCOreverse)
```

Make tables showing the proportion of topics/sex by Year.
```{r}

#Making a table that calculates the proportion of names by continent that make normal cutoff resrtictions.
PROP_NationA <- MCOcutoff %>% group_by(Continent) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), label=ifelse(Continent=="South America", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3), "Cutoff"= "Above/Equal to")

#Making a table that calculates the proportion of names by continent that get cutoff by restrictions. (Mutually exclusive from above)
PROP_NationB <- MCOreverse %>% group_by(Continent) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), label=ifelse(Continent=="South America", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3), "Cutoff"= "Below" )

#Making a table that calculates the continental distribution of all names from dataset
PROP_NationAll <- MCOb %>% group_by(Continent) %>% summarise(n=n())%>% mutate(freq= n/sum(n),cumul.sum = cumsum(freq), label=ifelse(Continent=="South America", paste0("N=", sum(n)),""),frequency = round(freq, digits = 3), "Cutoff"= "Total")
```

```{r}
#Matrix for statistical tests
Nationi <- rbind(MCOcutoff, MCOreverse)
#Matrix for graphing
Nation <- rbind(PROP_NationA,PROP_NationB,PROP_NationAll)
```

```{r}
jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig8.jpeg", quality=100,, width = 720, height = 480)
ggplot(Nation, aes(fill= Continent, x=Cutoff, y=freq)) + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("Microbiology First Author Continent of Residence based on Name-Sex Accuracy") +theme_classic()+ xlab("95% Accuracy, Samples=10")+ geom_text(aes(y=cumul.sum, label=label), vjust=-0.5, size=3)+ scale_y_continuous(labels = scales::percent) + scale_fill_manual(values=c("red4", "seagreen3","orange3","royalblue4","goldenrod1","orchid3"))+theme_light()+theme(text=element_text(size=15))
```

```{r}
chisq.test(Nationi$Cutoff, Nationi$Continent, correct= FALSE)
```


UNUSED FIGURES

------------------------------
Unused Figure Supplementary to 3A
```{r}
#Filtering Names into COVID vs. non-COVID papers

#Create a table with only the Biorxiv and Medrxiv covid-related papers
FC4<- bioRxivF_ %>% filter(Topic == "COVID") 

#Create a table with the opposite, remove any papers labelled "C" (As they are repeats)
FN4<- bioRxivF_ %>% filter(Topic != "COVID", Covid !="C") 


FN4$Year <- as.character(FN4$Year)

#Renaming non-covid 2020 papers to "2020 Other" 
FN4$Year[FN4$Year == "2020"] <- "2020 Other"

#Renaming COVID-19 Papers year to 2020 COVID-19 for Graphing 
FC4 <- mutate(FC4, Year = "2020 COVID-19")

Fig4 <- rbind(FC4,FN4) #Merge the two cells to recreate original table, now with no COVID-19 Paper repeats


fig4 <-Fig4 %>% group_by(Year, Sex) %>% summarise(n=n()) %>% mutate(freq= n/sum(n), cumsum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))%>% mutate(frequency = round(freq, digits = 3))

fig4$labelpos <- ifelse(fig4$Sex=="female", fig4$frequency/2, 1 - fig4$frequency/2)

#Plot4
#jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\Fig4.jpeg", quality=100, height=480, width= 720)
ggplot(fig4[order(fig4$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=factor(Year, levels=c("2017","2018","2019", "2020 Other", "2020 COVID-19" ) ), y=freq)) + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("Yearly First Author Sex Proportions") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumsum, label=label), vjust=-0.5, size=3)+xlab("Year")+theme_light()+theme(text=element_text(size=17))+ theme(legend.title = element_blank())
```

```{r}
ggplot(fig4[order(fig4$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ), x=factor(Year, levels=c("2017","2018","2019", "2020 Other", "2020 COVID-19" ) ), y=freq)) + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("Yearly First Author Sex Proportions") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumsum, label=label), vjust=-0.5, size=3)+xlab("Year")
```

UNUSED FIGURE SUPPLEMENTARY TO 3B
```{r}
LC4<- bioRxivL_ %>% filter(Topic == "COVID") 
LN4<- bioRxivL_ %>% filter(Topic != "COVID", Covid !="C") 
LN4$Year <- as.character(LN4$Year)
LN4$Year[LN4$Year == "2020"] <- "2020 Other"
LC4 <- mutate(LC4, Year = "2020 COVID-19")
Lig4 <- rbind(LC4,LN4) 
Lig4 <-Lig4 %>% group_by(Year, Sex) %>% summarise(n=n()) %>% mutate(freq= n/sum(n), cumsum = cumsum(freq), label=ifelse(Sex=="male", paste0("N=", sum(n)),""))%>% mutate(frequency = round(freq, digits = 3))
Lig4$labelpos <- ifelse(Lig4$Sex=="female", Lig4$frequency/2, 1 - Lig4$frequency/2)
#jpeg(file= "C:\\Users\\adamw\\Documents\\Gender Project\\Plots\\LFig4.jpeg", quality=100, height=480, width=720)
ggplot(Lig4[order(Lig4$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ),  x=factor(Year, levels=c("2017","2018","2019", "2020 Other", "2020 COVID-19" ) ), y=freq)) + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("Yearly Last Author Sex Proportions") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumsum, label=label), vjust=-0.5, size=3)
```

```{r}
ggplot(Lig4[order(Lig4$Sex, decreasing  = T),], aes(fill= factor(Sex, levels=c("male","female" ) ),  x=factor(Year, levels=c("2017","2018","2019", "2020 Other", "2020 COVID-19" ) ), y=freq)) + geom_bar(position="stack",stat="identity") + ylab("Percentage")+ggtitle("Yearly Last Author Sex Proportions") + scale_y_continuous(labels = scales::percent) +scale_fill_manual(values=c("royalblue1", "mediumorchid"))+ theme(legend.title = element_blank())+ geom_text(aes(label = paste0(100*frequency,"%"),y=labelpos),size = 4.5) + geom_text(aes(y=cumsum, label=label), vjust=-0.5, size=3)
```